---
title: "Lab 02 - Data wrangling and visualization"
subtitle: "Due: Friday, Jan 31 at 11:59pm"
author: ""
date: ""
output:
  pdf_document: default
  html_document: default
---

*****

You may knit this document to see what the template looks like. 
**When turning a document in on Gradescope, remember to `Knit to PDF`** and 
submit that PDF document. For Lab 02, we are not telling you when to commit -- 
it is up to you to commit at appropriate intervals with meaningful commit 
messages. Be sure to commit **at least three times** during this lab.

Delete everything between the 5 asterisks in your final document. Also, delete
the 5 asterisks.

*****

## Packages

```{r packages, warning = FALSE, message = FALSE}
library(tidyverse)
library(fivethirtyeight)
```

## Exercise 1

Type your answer to Exercise 1 here.

```{r}
### In this chunk, implement the code for Exercise 1.
### Name your chunk and then delete this comment.
```

## Exercise 2

```{r}
### In this chunk, implement the code for Exercise 2.
### Name your chunk and then delete this comment.

```

## Exercise 3

Type your answer to Exercise 3 here. There is no need for `R` code.

## Exercise 4

Add code and/or narrative as needed.

## Exercise 5

Add code and/or narrative as needed.

## Exercise 6

Add code and/or narrative as needed.

## Exercise 7

Add code and/or narrative as needed.

## Exercise 8

Add code and/or narrative as needed.

## Exercise 9

Add code and/or narrative as needed.

## Exercise 10

Add code and/or narrative as needed.


*****

## Final checks

1. Did you commit at least three times?
2. Do all code chunks have names?
3. Are your figures appropriately sized?
4. Does any resulting data frame show more than 20 rows? You should never
   print the entire data frame when it has a large number of rows.
5. Is all code and narrative following the 80 characters rule?
6. Did you proofread your narrative and run spell checker (button next to save)? 

*****



